### 2021-02-18 evaluation.tex
Reduce precision of factor to 3
Add results of final evaluation of combined model
nove poznamky k experimentum

\subsubsection{Metrics}
To analyze the training process,
we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
loss, accuracy and solver performance.
The solver performance was estimated once per 10 training epochs by running Vampire
on \num{1000} problems of the respective problem set
and counting the number of problems successfully solved within the time limit.
Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
Similarly, we are interested in generalization from training set to validation set.

@@

After the training finished,
we performed a final evaluation of the most promising intermediate trained model on the whole $\ProblemsVal$.
The model that manifested the best estimated solver performance was chosen as the most promising.
\todo{Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation.}

@@

A predicate precedence recommender was trained on approximately \num{500000} examples,
% Half of the 1M predicate examples was used for validation.
and a function precedence recommender was trained on approximately \num{400000} examples.
% Half of the 800k function examples was used for validation.
For each problem $P \in \ProblemsVal$,
a pair of symbol precedences was generated by the respective trained recommender
and Vampire was run using these precedences and a wall clock time limit of 10 seconds.
% Note: We have mentioned the time limit above and here we repeat it for readers who only read Results.
The results are averaged over 5 runs to reduce the effect of noise due to the wall clock time limit.
As a baseline, the performance of Vampire with the \texttt{frequency} precedence heuristic was evaluated
with the same time limit.
For comparison, the two trained recommenders are evaluated separately,
with the predicate precedence recommender using the \texttt{frequency} heuristic to generate the function precedences, and vice versa.

To generate a precedence for a problem,
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit is only imposed on the Vampire run
and excludes the time taken by the recommender to generate the precedence.
\todo{MS: and if we don't, this would be the perfect place to summarize
how long the just described procedure took on an average problem,
or how it (roughly) scales with the graph/cnf/tptp\_file size.}
When run with 1 thread on 1000 problems,
the preprocessing took 1 second on average and at most 5 seconds,
increasing linearly with the number of nodes of the graph representation of the problem.
\todo{FB: Measure the times with joint recommender and TF restricted to 1 thread. Fix the numbers once we have a solid measurement. Add a comment with a reference to the data.}

@@

\acrshort{gcn} (predicate and function) &&&&\\
% VML-706

@@

\num[round-mode=places,round-precision=4]{1.040853141} \\

@@

\num[round-mode=places,round-precision=4]{1.027748302} \\

@@

\num[round-mode=places,round-precision=4]{1.0} \\

>>>>

\subsubsection{Metrics}
To analyze the training process,
we tracked the dynamics of three metrics on $\ProblemsTrain$ and $\ProblemsVal$:
loss, accuracy and solver performance.
The solver performance was estimated once per 10 training epochs by running Vampire
on \num{1000} problems of the respective problem set
and counting the number of problems successfully solved within the time limit.
Since the accuracy is a proxy measure of solver performance and the loss is a proxy measure of the accuracy,
we are interested in generalization from loss to accuracy and from both loss and accuracy to solver performance.
Similarly, we are interested in generalization from training set to validation set.
\todo{MS: kdyz se to tady tak pekne pripravi, asi ctenar ceka, ze se to pozdeji 
nejak zuzitkuje. Pokud se rozhnodnem loss/accuracy/ATP zavislost dal nerozebirat,
asi je tu navic i tento odstavec, nebo aspon jeho cast.}

@@

After the training finished,
we performed a final evaluation of the most promising intermediate trained model on the whole $\ProblemsVal$.
The model that manifested the best estimated solver performance was chosen as the most promising.
\todo{Watch out: This way we may overfit on the 1000 problems used for sample solver performance evaluation.}
\todo{MS: taky me to ted napadlo! Uplne oficialni metodika byva split na train,valid,test. 
Kdy se trenuje na train, hyperparametry (vcetne early stopping) se ladi vuci valid 
a pak se vyhodnocuje na test. Nekdy se pak valid rika devel a test se rika holdout.}

@@

A predicate precedence recommender was trained on approximately \num{500000} examples,
% Half of the 1M predicate examples was used for validation.
and a function precedence recommender was trained on approximately \num{400000} examples.
% Half of the 800k function examples was used for validation.
For each problem $P \in \ProblemsVal$,
a pair\todo{MS: ja vim, ze sis to "vyplejtval" v predchozi vete,
ale kde jinde nez tady rict explicitne "predicate precendence" a "function precedence"?
Z toho "pair" ot nemusi byt jasny...}
 of symbol precedences was generated by the respective trained recommender
and Vampire was run using these precedences and a wall clock time limit of 10 seconds.
% Note: We have mentioned the time limit above and here we repeat it for readers who only read Results.
The results are averaged over 5 runs to reduce the effect of noise due to the wall clock time limit.
As a baseline, the performance of Vampire with the \texttt{frequency} precedence heuristic was evaluated
with the same time limit.
For comparison, the two trained recommenders are evaluated separately,
with the predicate precedence recommender using the \texttt{frequency} heuristic to generate the function precedences, and vice versa.

To generate a precedence for a problem,
\todo{MS: tenhle odstavec mozna prehodit s predchozim?}
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit is only imposed on the Vampire run
and excludes the time taken by the recommender to generate the precedence.
\todo{MS: and if we don't, this would be the perfect place to summarize
how long the just described procedure took on an average problem,
or how it (roughly) scales with the graph/cnf/tptp\_file size.}
When run with 1 thread on 1000 problems,
\todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
2) kterych 1000? To opet drazdi k otazkam. tj to bych asi taky vynechal, ale...
3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
the preprocessing took 1 second on average and at most 5 seconds,
increasing linearly with the number of nodes of the graph representation of the problem.
\todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
\todo{FB: Measure the times with joint recommender and TF restricted to 1 thread.
 Fix the numbers once we have a solid measurement.
 Add a comment with a reference to the data.}
 \todo{MS: To by bylo taky fajn!}

@@

\acrshort{gcn} (predicate and function) &
% VML-706

\num{3951.6} &
\num[round-mode=places,round-precision=2]{1.624807680927192} &
\SI{51.69}{\percent} &
\num[round-mode=places,round-precision=3]{1.048280985} \\

@@

\num[round-mode=places,round-precision=3]{1.040853141} \\

@@

\num[round-mode=places,round-precision=3]{1.027748302} \\

@@

\num[round-mode=places,round-precision=3]{1.0} \\
